%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj + some brand new features from Mary Feofanova
% Website: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{0pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  linkbordercolor=red,
  urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
  \item\small{
  	\ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
  }
}

% \usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}

\newcommand{\resumeSummerySubheading}[4]{
\small
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
      {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{2pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large{Ivan Nasonov}} & Github: \href{https://github.com/NasonovIvan}{NasonovIvan} \quad LinkedIn: \href{https://www.linkedin.com/in/ivan-nasonov/}{Ivan Nasonov}\\
  \textbf{Data Scientist} & Email : \href{nasonov.ia18@physics.msu.ru}{nasonov.ia18@physics.msu.ru} \quad Mobile : +7\hspace{0.5ex}996\hspace{0.5ex}793\hspace{0.5ex}34\hspace{0.5ex}12 \\
\end{tabular*}

%----------SUMMARY-----------------
\section{Summary}
    % \resumeSummerySubheading
    \small{
    Physics graduate with a Bachelor's degree from MSU, currently pursuing a Master's degree. Skilled in machine learning (RL, CV, TR, RNN) for solving control problems, image recognition, and sequence classification. Published 1 article in Automation and Remote Control journal, with 2 more in progress. Completed 7 ML projects, demonstrating strong practical experience. Collaborative team player with a 2nd place win in the All-Russian Hackathon for Telegram Bots.}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeExpSubheading
      {Institute of Control Sciences of Russian Academy of Sciences}{Moscow, RU}
      {Data Scientist, Engineer of lab. control based on incomplete data}{Oct. 2021 - Present}
      {\skill{Python} \skill{TensorFlow}}
      \resumeDesc{
      \begin{itemize}
          \item Leveraging machine learning (RL, CV, TR, RNN) for addressing control problems, image recognition, and sequence classification, with presentations at All-Russian conferences on control systems and mathematical theory of control.
      \end{itemize}
      }
      \resumeExpSubheading
      {GreenEco Investments}{Moscow, RU}
      {\makecell[l]{Data Analyst team}}{\makecell[r]{May 2021 - Mar. 2022}}
      {\skill{Climate research}}
      \resumeDesc{\begin{itemize}
          \item Engaged in reducing emissions, decarbonization, and forest/peat bog expansion projects while collaborating with Joint Crediting Mechanism, VERRA, Gold Standard, and Climate Action Reserve, and performing carbon market analysis.
      \end{itemize}}
  \resumeSubHeadingListEnd

%----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeProjSubheading
      {\href{https://github.com/NasonovIvan/NN-whale-recognition}{Neural Network For Whale Detection}}{Moscow, RU}
      {\skill{Python} \skill{TensorFlow}}{Dec. 2022 - Mar. 2023}
          \resumeDesc{Transfer learning of the Xception network was used for recognizing and classifying whale voices using spectrograms.}
          
      \resumeProjSubheading
      {\href{https://github.com/NasonovIvan/ROTI-map-forecast}{ROTI Maps Daily Prediction}}{Moscow, RU}
      {\skill{Python} \skill{TensorFlow}}{Sept. 2022 - Jan. 2023}
          \resumeDesc{Using deep learning and Recurrent Neural Networks, daily prediction and synthesis of ROTI maps based on geomagnetic and solar indices were obtained.}
      
  \resumeSubHeadingListEnd

%----------Achievements-----------------
\section{Achievements}
  \resumeSubHeadingListStart
          
    \resumeProjSubheading
      {\href{https://github.com/NasonovIvan/BookingBot21}{Weeklython} - II place [All-Russian Hackathon]}{Moscow, RU}
      {\skill{Python} \skill{SQLAlchemy} \skill{Web UI}}
      {Aug. 2022}
          \resumeDesc{Developed Telegram bot for booking School Objects. The project contains CI/CD technology, Database project, IDEF0 diagram, UI/UX project in Figma.}
          
    \resumeProjSubheading
      {\href{https://github.com/NasonovIvan/Marusia}{Marusia Game Challenge} - Prize-winning place [Hackathon VK]}{Moscow, RU}
      {\skill{C++}}
      {Aug. 2020}
          \resumeDesc{Algorithmic solution finding in games for training the voice assistant Marusia of VK company.}
  \resumeSubHeadingListEnd
%--------Publications------------
  \section{Publications}
  \resumeSubHeadingListStart
  \item{\href{https://www.researchgate.net/publication/369658302_Neural_Network_Algorithm_for_Intercepting_Targets_Moving_Along_Known_Trajectories_by_a_Dubins'_Car}{\textbf{Neural Network Algorithm for Intercepting Targets Moving Along Known Trajectories by a Dubins’ Car}}
   }\vspace{-2pt}
 \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {Lomonosov Moscow State University}{Moscow, RU}
       {Master's degree in Physics}{Sept. 2022 - Aug. 2024 (Present)}
    \resumeSubheading
      {Lomonosov Moscow State University}{Moscow, RU}
      {Bachelor of Physics}{Sept. 2018 - Jul. 2022}
	\resumeItemListStart
        \resumeItem{Thesis}
          {{\href{https://github.com/NasonovIvan/pursuit-evasion-problem}{A neural network algorithm for intercepting targets moving along known trajectories by a Dubins' machine.}}}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
  

%-----------ADDITIONAL EDUCATION-----------------
\section{Additional Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {School21 -- peer-to-peer coding school fostering practical learning}{Moscow, RU}{Programming school}{Apr. 2022 - Jun. 2024 (Present)}
    \resumeSubheading
       {deeplearning.ai}{Coursera}{The Deep Learning Specialization}{Mar. 2020 - May 2020}
    \resumeItemListStart
        \resumeItem{Subjects}
          {Neural Networks and Deep Learning; Hyperparameter tuning, Regularization and Optimization; Convolutional Neural Networks; Sequence Models; Recurrent Neural Networks}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \begin{itemize}[leftmargin=0.1in]
 \setlength\itemsep{0.5em}
   \item{
     \textbf{Languages}{: C, C++, Python, Bash }
   }\vspace{-7pt}
   \item{
     \textbf{Technologies}{: ML, DL, RL, CV, TR, SQL, Git, \LaTeX, MPI for Python }
   }
   \vspace{-7pt}
   \item{
     \textbf{Knowledge}{: Algorithms, Data Structures, Parallel Programming}
   }
 \end{itemize}


%-------------------------------------------
\end{document}
